Simulations of Ballot Polling Risk-Limiting Audits

### 2021-11-02 MultipleRoundSims/sections/01-intro.tex
rephrase

\Minerva was designed for R2 audits and applies its stopping rule once for each round. Thus it does not require the tracking of ballots that SO \BRAVO does. Zag{\'o}rski {\em et al.} \cite{usenix_minerva} prove that \Minerva is a risk-limiting audit and requires fewer ballots to be sampled than EoR \BRAVO when an audit is performed in rounds and the round schedule is pre-determined (before any ballots are drawn). They also present first-round simulations which show that \Minerva draws fewer ballots than SO \BRAVO in the first round for large first rounds when the (true) underlying election is as announced.

>>>>

\Minerva was designed for R2 audits and applies its stopping rule once for each round. Thus it does not require the tracking of ballots that SO \BRAVO does. Zag{\'o}rski {\em et al.} \cite{usenix_minerva} prove that \Minerva is a risk-limiting audit and requires fewer ballots to be sampled than EoR \BRAVO when an audit is performed in rounds and the round schedule is pre-determined (before any ballots are drawn). They also present first-round simulations which show that \Minerva draws fewer ballots than SO \BRAVO in the first round for first round sizes with a large probability of stopping when the (true) underlying election is as announced.
